\section{Push Feedback Workflow}\label{sec:push-workflow}

The feedback workflow for pull-requests is invoked for pull-requests that target
protected branches.  The push feedback workflow is invoked for when scans of protected
branches are completed.  This would typically indicate that the code in the branch
is appropriate for deployment and thus risk for unresolved vulnerabilities is acceptable.

At the completion of a scan on a protected branch, a Sarif log is generated using the
\cxonesarif Python module.  The contents of the generated log is then delivered to one
or more endpoints as configured.  The receiver is then responsible for interpreting the
Sarif log contents and performing any additional workflows that may catalog the
scan results.


\subsection{Common Log Delivery Message Headers}
Delivery of a scan's Sarif log is performed by delivering the log to a receiver
endpoint via \intlink{sec:push-sarif-amqp}{AMQP} and/or \intlink{sec:push-sarif-http}{HTTP}
transports.  Each of these methods will deliver a Sarif log or error message as appropriate for
the scan disposition.  As part of the delivered message, Table \ref{tab:common-push-feedback-headers}
enumerates header key/value pairs that are sent along with the message body.  The headers can be accessed
with methods appropriate for the transport method.

\begin{table}[ht]
    \caption{Common Push Feedback Message Headers}  
    \label{tab:common-push-feedback-headers}      
    \begin{tabularx}{\textwidth}{ll}
        \toprule
        \textbf{Header} & \textbf{Description} \\
        \midrule
        \texttt{x-cx-signature} & \makecell[l]{The HMAC signature of the raw binary of the message body.} \\
        \midrule
        \texttt{x-cx-signature-alg} & \makecell[l]{The HMAC algorithm used to produce the signature value in the\\\texttt{x-cx-signature} header.}\\
        \midrule
        \texttt{x-cx-scanid} & \makecell[l]{The \cxone scan id that was used to generate the contents\\of the message.}\\
        \midrule
        \texttt{x-cx-projectid} & \makecell[l]{The \cxone project id where the scan can be found.}\\
        \midrule
        \texttt{x-cx-service} & \makecell[l]{The \cxoneflow service definition that handled the webhook event\\that performed the scan.}\\
        \midrule
        \texttt{x-cx-clone-url} & \makecell[l]{The clone URL for the code repository that was scanned.}\\
        \midrule
        \texttt{x-cx-branch} & \makecell[l]{The branch of the code repository for which the scan was executed.}\\
        \midrule
        \texttt{x-cx-commit} & \makecell[l]{The git commit hash of the code that was scanned.}\\
        \midrule
        \texttt{x-cx-is-error} & \makecell[l]{A boolean value indicating if the message body is an error message.}\\
        \midrule
        \bottomrule
    \end{tabularx}
\end{table}


\subsection{Scan Error Message Delivery}

\subsection{AMQP Sarif Log Delivery}\label{sec:push-sarif-amqp}

The AMQP delivery is performed by posting a message to an \extlink{https://www.rabbitmq.com/docs/exchanges}{exchange} with a routing key
consisting of the name of the service definition that orchestrated the scan.  This allows multiple queues to bind to the exchange
so that the message is sent to queues using the routing key match criteria defined in the binding.


\subsection{HTTP Sarif Log Delivery}\label{sec:push-sarif-http}
If the HTTP endpoints are unstable or there are many, consider receipt of the log
by many endpoints by using AMQP.



\subsection{Sender Verification with HMAC}
The method of authenticating the sender is to validate a signature hash calculated
from the body of the delivered message.  This is done using a secret value
known by both the sender and receiver.  There is no need for sender and receiver to
exchange the shared secret; the signature verification allows each side to demonstrate
knowledge of the shared secret by producing the same calculated signature.

If the signatures match, it is verified the sender and receiver both know the same
shared secret.  If the signatures don't match, the received message is typically
discarded since the sender can't be verified by demonstrating knowledge of a
mutually shared secret.  The data integrity is also ensured given the signature
of the received body content would not have a matching signature if it was
modified in transit.

The signature is typically validated prior to processing the received contents.  This
allows data sent by unverified senders or data that was modified in transit to be
discarded.

\subsubsection{AMQP Example}

The example code for demonstrating HMAC signature validation with an AMQP receiver
consumes a pre-defined queue that has been bound to a pre-defined exchange. Sarif logs are
delivered to the exchange and the queue is bound to the exchange.  Agents that consume
the queue are given messages from the queue to handle as appropriate.

The example reads the signature and algorithm from the received message headers.
The receiver, which also knows the shared secret used to calculate the signature
by the sender, recalculates the signature on the received message content.  If the signatures
match, the message is verified as sent by the correct sender.


\begin{code}{HMAC Verification Example}{[AMQP]}{}
import hmac
import asyncio, aio_pika

# An example of how to verify the HMAC signature
# of the received Sarif log body.

async def receive_sarif_log(msg: aio_pika.abc.AbstractIncomingMessage) -> None:
    try:
       
      shared_secret = "MySharedSecret-12344$abc!123"
      sig = msg.headers['x-cx-signature']
      alg = msg.headers['x-cx-signature-alg']
      print(f"Received message with signature: {sig} generated using algorithm {alg}")

      h = hmac.new(bytes(shared_secret, 'UTF-8'), msg.body, alg)
      if h.hexdigest() != sig:
          print(f"Calculated signature {h.hexdigest()} is invalid.")
      else:
        print("The signature verified correctly.")

    except BaseException as ex:
        await msg.nack(requeue=False)
    finally:
        await msg.ack()

async def be_an_agent():
  mq_client = await aio_pika.connect_robust("amqp://localhost/sarif")
  async with mq_client.channel() as channel:
      q = await channel.get_queue("SARIF")
      await q.consume(receive_sarif_log)
      while True:
          await asyncio.Future()

if __name__ == "__main__":
  asyncio.run(be_an_agent())
\end{code}



\subsubsection{HTTP Example}

The example code for demonstrating HMAC signature validation with an HTTP receiver
is a simple Flask application. The application acts as an HTTP receiver endpoint
for receiving Sarif logs.  The example reads the signature and algorithm from the request
headers.  The receiver, which also knows the shared secret used to calculate the signature
by the sender, recalculates the signature on the received body content. If the signatures
match, the message is verified as sent by the correct sender.


\begin{code}{HMAC Verification Example}{[HTTP]}{}
import hmac
from flask import Flask, request, Response

# An example of how to verify the HMAC signature
# of the received Sarif log body.

app = Flask("Example")

@app.route("/sarif", methods=['POST'])
async def validate__hmac_signature():
    shared_secret = "MySharedSecret-12344$abc!123"
    sig = request.headers['x-cx-signature']
    alg = request.headers['x-cx-signature-alg']
    print(f"Received message with signature: {sig} generated using algorithm {alg}")

    h = hmac.new(bytes(shared_secret, 'UTF-8'), request.data, alg)
    if h.hexdigest() != sig:
        print(f"Calculated signature {h.hexdigest()} is invalid.")
        return Response(status=403)
    else:
      print("The signature verified correctly.")
      return Response(status=204)

\end{code}



